Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-30 ms.tex
correct best-fit absolute zero level regression result to account for 0.3% bandpass correction fix
propagate change in bandpass corrections to best-fit preprocessing parameters in Table 1

Specifically, we perform a linear fit to the FDS99-predicted 857 GHz values as 
a function of \PLANCK~857 GHz. For this purpose, we employ a version of the 
\PLANCK~857 GHz map with zodiacal light and point sources removed and smoothed 
to 1$^{\circ}$ FWHM, which we will refer to as $\mathcal{I}_{857}$. We 
consider $\mathcal{I}_{857}$ to be the independent variable, as it has much 
higher S/N than the FDS99 prediction, henceforward referred to as 
$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not simply the FDS99
model evaluated at 857 GHz, but also incorporates the color correction factor 
of $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine the dust 
spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels with 
$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
resolution has very high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 
$\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
fit overplotted. The linear fit was performed with uniform weights and 
iterative outlier rejection. The best-fit linear model is given by 
$\mathcal{F}_{857}$=0.994$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
the slope is quite close to unity, and the offset near zero.

@@

\begin{deluxetable*}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{table:offs} Planck/IRAS Map Properties \& Pre-processing} 
\tablehead{
\colhead{$\nu$ (GHz)} &
\colhead{Offset ($K_{CMB}$)} & 
\colhead{Dipole ($K_{CMB}$)} & 
\colhead{Quadrupole ($K_{CMB}$)} & 
\colhead{$c_{\nu}$} &
\colhead{FWHM ($'$)}
}
\startdata
100 & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & $-$7.17$\times$10$^{-6}$ &  0.0054 & 9.66 \\
143 & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & - & 0.0054 &  7.27 \\
217 & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & - & 0.0054 &  5.01 \\
353 & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & - & 0.012 & 4.86 \\
    & Offset (MJy/sr) & Dipole (MJy/sr) & Quadrupole (MJy/sr) & & \\ \cline{2-4} \\ [-2ex]
545 & 7.28$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$  & - & 0.10 & 4.84 \\
857 & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ &  - & - & 0.10 & 4.63 \\
3000 & 0.0$\pm$4.3$\times$10$^{-2}$ & - & - & 0.10 & 6.1
\enddata
\end{deluxetable*}

>>>>

Specifically, we perform a linear fit to the FDS99-predicted 857 GHz values as 
a function of \PLANCK~857 GHz. For this purpose, we employ a version of the 
\PLANCK~857 GHz map with zodiacal light and point sources removed and smoothed 
to 1$^{\circ}$ FWHM, which we will refer to as $\mathcal{I}_{857}$. We 
consider $\mathcal{I}_{857}$ to be the independent variable, as it has much 
higher S/N than the FDS99 prediction, henceforward referred to as 
$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not simply the FDS99
model evaluated at 857 GHz, but also incorporates the color correction factor 
of $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine the dust 
spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels with 
$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
resolution has very high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 
$\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
fit overplotted. The linear fit was performed with uniform weights and 
iterative outlier rejection. The best-fit linear model is given by 
$\mathcal{F}_{857}$=0.991$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
the slope is quite close to unity, and the offset near zero.

@@

\begin{deluxetable*}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{table:offs} Planck/IRAS Map Properties \& Pre-processing} 
\tablehead{
\colhead{$\nu$ (GHz)} &
\colhead{Offset ($K_{CMB}$)} & 
\colhead{Dipole ($K_{CMB}$)} & 
\colhead{Quadrupole ($K_{CMB}$)} & 
\colhead{$c_{\nu}$} &
\colhead{FWHM ($'$)}
}
\startdata
100 & 1.69$\times$10$^{-5}$$\pm$3.61$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & $-$7.17$\times$10$^{-6}$ &  0.0054 & 9.66 \\
143 & 3.58$\times$10$^{-5}$$\pm$7.58$\times$10$^{-7}$ & $-$1.08$\times$10$^{-5}$ & - & 0.0054 &  7.27 \\
217 & 7.79$\times$10$^{-5}$$\pm$2.60$\times$10$^{-6}$ & $-$1.40$\times$10$^{-5}$ & - & 0.0054 &  5.01 \\
353 & 2.76$\times$10$^{-4}$$\pm$1.95$\times$10$^{-5}$ & $-$3.08$\times$10$^{-5}$ & - & 0.012 & 4.86 \\
    & Offset (MJy/sr) & Dipole (MJy/sr) & Quadrupole (MJy/sr) & & \\ \cline{2-4} \\ [-2ex]
545 & 7.27$\times$10$^{-2}$$\pm$1.99$\times$10$^{-2}$ & 1.63$\times$10$^{-2}$  & - & 0.10 & 4.84 \\
857 & 1.82$\times$10$^{-2}$$\pm$6.02$\times$10$^{-2}$ &  - & - & 0.10 & 4.63 \\
3000 & 0.0$\pm$4.3$\times$10$^{-2}$ & - & - & 0.10 & 6.1
\enddata
\end{deluxetable*}
